%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Associate} % Job title
    {\emph{GENPACT}} % Organization
    {Gurugram} % Location
    {Nov. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built machine-learning models and NLP systems using client's proprietary data assets in manufacturing analytics.}
        \item {Conducted machine-learning training sessions and contributed to Budding Analytics.}
        \item {Automated financial reports which are developing into software offering.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DATA SCIENTIST} % Job title
    {Numetric Technologies} % Organization
    {Gurugram} % Location
    {May 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a real time web scraper to alert the client if the prices of certain commodities fluctuates more than a threshold.}
        \item {Implemented a data mining project to help build an engine to facilitate modeling and analysis of historical data.}
        \item {Facilitated the development of a web extension which provides near real time game statistics to help attract more audience.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
	{co-founder}
	{TNine Infotech}
	{New Delhi}
	{Jul. 2015 - Dec. 2015}
	{
		\begin{cvitems}
			\item {Overhauled business strategy, managed clients \& assisted in web development.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
    {Software Developer Intern}
    {Impact Ventures}
    {New Delhi}
    {Feb. 2015 - May 2015}
    {
	  \begin{cvitems}
		  \item {Worked on the development of back-end system software for an app to pave way for skill development in customer service industry.}
	  \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
   {Research Intern}
   {Bhabha Atomic Research Centre (BARC)}
   {Vizag}
   {Jun. 2013 - Aug. 2013}
   {
 	 \begin{cvitems}
 	 	\item {Worked on an IEMA in the Computational Analysis Division at BARC. IEMA accelerates objects with predetermined velocity towards specific targets. Projects to aid investigations and gain basic insight of tools and techniques used to operate an EM system were performed.}
 	 \end{cvitems}
   }

%---------------------------------------------------------
\end{cventries}
